Investigating Determinism of Physics Engines for usage in CAV and V\&V simulations

### 2021-10-28 document/source/body.tex
final changes

\subsubsection{Determinism}
Schumann et al.\ describe determinism as the property of causality given a temporal development of events such that any state is completely determined by prior states~\cite{Schumann2010}.\TODO{KIE: I can't find that quote in that paper, please point me to it.} However, in the context of simulation this should be expanded to include not just prior states but also the history of actions taken by all actors. Therefore, a deterministic simulation will always produce the same result given the same history of prior states and actions.

>>>>

\subsubsection{Determinism}
Schumann et al.\ describe determinism as the property of causality given a temporal development of events such that any state is completely determined by prior states~\cite{Schumann2010}. However, in the context of simulation this should be expanded to include not just prior states but also the history of actions taken by all actors. Therefore, a deterministic simulation will always produce the same result given the same history of prior states and actions.
